### 2020-11-15 end_appendix/appendix.tex
Optimized style

>>>>

\subsection{test}

\subsubsection{test}

\paragraph{hi}

The \ac{ECS} is really cool. I like it very much!

This is e.g. without an "at" and this is it with an "at" e.g.\@ difference? Test space. Real dot!

These are really cool papers: \autocite{Schlund2020, Schlund2020a}

And this one, too: \autocite{Lauer2020}

\texttt{input <iostream>}

\begin{equation}
  c_{k_1,k_2} := 1200 \, \log_2 \left( \frac{f_1^{(k_2)}}{f_1^{(k_1)}} \right) \unit{cents}. \label{eq:2:cent_def}
\end{equation}

\begin{table}
  \caption{The effects of treatments X and Y on the four groups studied.}
  \label{tab:treatments}
  \centering
  \begin{tabular}{l l l}
    \toprule
    \tabhead{Groups} & \tabhead{Treatment X} & \tabhead{Treatment Y} \\
    \midrule
    1 & 0.2 & 0.8\\
    2 & 0.17 & 0.7\\
    3 & 0.24 & 0.75\\
    4 & 0.68 & 0.3\\
    \bottomrule\\
  \end{tabular}
\end{table}

\begin{table}[t]
  \centering
  \begin{tabular}{c l r r}
    \toprule
    Semitones & Interval & $c/\unit{cents}$ (ET) & $c/\unit{cents}$ (JI) \\
    \midrule
    $0$ & Perfect unison & $0$ & $0$ \\
    $1$ & Minor second & $100$ & $112$ \\
    $2$ & Major second & $200$ & $204$ \\
    $3$ & Minor third & $300$ & $316$ \\
    $4$ & Major third & $400$ & $386$ \\
    $5$ & Perfect fourth & $500$ & $498$ \\
    $6$ & Augmented fourth & $600$ & $590$ \\
    $7$ & Perfect fifth & $700$ & $702$ \\
    $8$ & Minor sixth & $800$ & $814$ \\
    $9$ & Major sixth & $900$ & $884$ \\
    $10$ & Minor seventh & $1000$ & $996$ \\
    $11$ & Major seventh & $1100$ & $1088$ \\
    $12$ & Perfect octave & $1200$ & $1200$ \\
    \bottomrule
  \end{tabular}
  \caption{Logarithmic frequency ratios $c$ of certain intervals in the equal temperament (ET) and the just intonation (JI). $x$ cents correspond to a frequency ratio of $2^{\, x/1200}$.}
  \label{tab:2:cents}
\end{table}
